---
title: "Retail"
author: "Ayodeji Akiwowo"
date: "31 October 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Big Mart Sales
The Big Mart Sales Prediction was an online Data Science hackhathon on [Analytics Vidhya](https://datahack.analyticsvidhya.com/contest/black-friday/#data_dictionary)

**Problem Statement**

*A retail company “ABC Private Limited” wants to understand the customer purchase behaviour* *(specifically, purchase amount) against various products of different categories. They have shared* *purchase summary of various customers for selected high volume products from last month.*
*The data set also contains customer demographics (age, gender, marital status, city_type,* *stay_in_current_city), product details (product_id and product category) and Total purchase_amount from* *last month.*
*Now, they want to build a model to predict the purchase amount of customer against various products* *which will help them to create personalized offer for customers against different products.*



```{r, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
